### 2015-02-04 cav-2015-tex/approach.tex
Simplified definitions and corrected a few minor errors.

The symbolic heap algorithm only partitions the heap at points of
divergence in the control flow graph such as comparisons of references
(program control flow) and field dereferences or writes (execeptional
control flow due to null pointers). There are three sets of rewrite
rules specific to the symbolic heap algorithm: (i) rules to initialize
symbolic references, (ii) rules to perform field dereferences and
writes, and (iii) rules to check equality and inequality of
references.

>>>>

The symbolic heap algorithm only partitions the heap at comparison
operations or for exception handling. 
There are three sets of rewrite
rules specific to the symbolic heap algorithm: (i) rules to initialize
symbolic references, (ii) rules to perform field dereferences and
writes, and (iii) rules to check equality and inequality of
references.

### 2015-02-04 cav-2015-tex/bisimulation.tex
Simplified definitions and corrected a few minor errors.

\section{Bisimilarity Proof}
\label{sec:bisim}
The theoretical result is the existence of a bisimulation between
states related by GSE with lazy initialization ($p \rgse p^\prime$)
and states related by the algorithm in this paper ($q \rsym q^\prime$). The relations are on the universe of \emph{well-formed} states $S$, which have the
properties in \secref{sec:sh} with the constraint that
the states are \emph{feasible}: successors exist unless at
\cfgt{end}. Let $p \rgse p^\prime$ be a union over relations for GSE (see appendix):
$\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access after evaluating the expression for
the base reference $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow
\cfgnt{k}\rp$, \emph{W} is a field write after evaluating the
expression for the right operand $\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the
left and right operands $\lp \cfgnt{v}\ \cfgt{=}\ \cfgnt{*}
\rightarrow \cfgnt{k}\rp$, the prime symbol indicates a null reference
in the operation or a false outcome, and \emph{\com} is everything
else in the language. Any state relation, say $\rightarrow_x$, is
trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
The relation captures the notion of splitting groups of heaps at
certain operations. For example, suppose we have a set $P$ containing a single state $p$
with all references uninitialized. If $p$ is a field access state, it has two
potential successors in GSE: a non-null reference and a null reference. 
Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.

>>>>

\section{Bisimilarity Proof}
\label{sec:bisim}
The theoretical result is the existence of a bisimulation between sets of states
states related by GSE ($p \rgse p^\prime$)
and states related by the algorithm in this paper ($q \rsym q^\prime$). The relations are on the universe of \emph{well-formed} states $S$, which have the
properties in \secref{sec:sh} with the constraint that
the states are \emph{feasible}: successors exist unless at
\cfgt{end}. Let $p \rgse p^\prime$ be a union over relations for GSE (see appendix):
$\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access after evaluating the expression for
the base reference $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow
\cfgnt{k}\rp$, \emph{W} is a field write after evaluating the
expression for the right operand $\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the
left and right operands $\lp \cfgnt{v}\ \cfgt{=}\ \cfgnt{*}
\rightarrow \cfgnt{k}\rp$, the prime symbol indicates a null reference
in the operation or a false outcome, and \emph{\com} is everything
else in the language. Any state relation, say $\rightarrow_x$, is
trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
The relation captures the notion of splitting groups of heaps at
certain operations. For example, suppose we have a set $P$ containing a single state $p$
with all references uninitialized. If $p$ is a field access state, it has two
potential successors in GSE: a non-null reference and a null reference. 
Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.
